---
title: "ML project"
author: "Shaked"
date: "February 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, load the training and test data
```{r, cache=TRUE}
raw_training <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
raw_test <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
```
clean up the data: Some columns are almost entirely comprised of missing values, so we eliminate those. We also eliminate the index, timestamp, and window variables (which are dependant on the classe).
```{r}
eliminator <- function(col) {sum(is.na(col))/length(col)<0.8 && sum(col=="")/length(col)<0.8 &&  !("#DIV/0!" %in% col)}
goodcols <- sapply(raw_training,eliminator)
raw_training <- raw_training[goodcols]
raw_test<- raw_test[goodcols]

badcols = c("X","user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","new_window","num_window")
raw_training <- raw_training[!names(raw_training) %in% badcols]
raw_test <- raw_test[!names(raw_test) %in% badcols]
```

Split the raw training data into training and validation sets

```{r, cache=TRUE}
require(caret)
set.seed(5423)
inTrain = createDataPartition(raw_training$classe, p = 3/4)[[1]]


training = raw_training[ inTrain,]
validation = raw_training[-inTrain,]
```

First, check what happens if we train a random forest on the training data
```{r, cache=TRUE}
require(randomForest)
set.seed(34532)
forest_model <- randomForest(classe~.,data=training)
#Check the accuracy on the validation set
sum(predict(forest_model,validation)==validation$classe)/length(validation$classe)
```

Next, check an lda model
```{r, cache=TRUE}
require(caret)
set.seed(2345)
lda_model <- train(classe~.,data=training,method="lda")
#Check the accuracy on the validation set
sum(predict(lda_model,validation)==validation$classe)/length(validation$classe)
```

As we see, the random forest model is significantly more accurate than the lda model. Finally, we use it to predict on the test data:

```{r}
predict(forest_model,raw_test)
```







